Using traffic analysis to identify The Second Generation Onion Router

### 2011-01-30 thesis/thesis.tex
Remove more erroneous page prefixes in citations, remove emphasis everywhere - using it wrongly

The possibility of public key cryptography, or \emph{non-secret
encryption} was conceived by James H. Ellis in \citeyear{Ellis:1970p3249} and
later developed into both a method for sharing secret encryption keys by
Malcolm J. Williamson in 1974 \parencite{Singh:1999:CBE} and a method for
asymmetric encryption \parencite{Cocks:1973p3265}.

@@

The first anonymous network system MixNet, was described in
\textcite{Chaum:1981p296}. This proposal makes essential usage of public key
encryption to prevent eavesdroppers from obtaining message delivery information.
Senders in the network communicate with a centrally located server known as a
\emph{mix}, delivering a message with the address of the intended recipient. The
mix server discards any information about the sender and delivers it to the
final destination. Figure \ref{chaums-mix-network} depicts the process of
message delivery in Chaum's MixNet. Chaum's proposal also allowed for the
chaining of multiple mix servers together to form a \emph{cascade}.

@@

\begin{itemize*}
  \item Anonymous remailers such as \emph{Babel} \parencite{Gulcu:1996p1662}
    and \emph{Mixminion} \parencite{Danezis:2003ys}.
  \item Networks that provide mathematically provable anonymity
    \parencite{Chaum:1988p5869,Waidner:1989p5870,Berman:2004p303}.
  \item Anonymity that degrades gracefully when subject to attack, so called
    \emph{robust anonymity} \parencite{Waidner:1989p5870,Jakobsson:1998p5137}.
  \item Anonymous publishing in \emph{Freedom} \parencite{Goldberg:1999p2231}
    and \emph{Freenet} \parencite{Clarke:2001p2435}.
  \item Peer to Peer (P2P) anonymity such as \emph{MorphMix}
    \parencite{Rennhard:2002p4559}, \emph{Tarzan} \parencite{Freedman:2002kx} and
    \emph{P5} \parencite{P5Sherwood:2005p5872}.
  \item Censorship resistance in \emph{aChord} and \emph{gnuNet}
    \parencite{Hazel:2002p6929}, \emph{Infranet} \parencite{Feamster:2002p307}
    and of course Tor.
\end{itemize*}

@@

Like MixNet, public key cryptography is combined with intermediate servers
responsible for message delivery to provide a degree of anonymity. In Tor,
these mixes are known as \emph{relays} and are typically chained together to
construct a \emph{circuit}. Clients connect to the Tor network by communicating
with a special relay known as a \emph{bridge}, which constitutes the first
relay in a circuit. Traffic is repeatedly delivered through relays until it
reaches another special relay known as an \emph{exit node}, where it is
delivered unencrypted to the final destination. Figure \ref{tor-network} shows
this typical usage of the Tor network.

@@

Messages delivered through the Tor network are encrypted multiple times using a
variation of onion routing \parencite{Michael:2001} known as \emph{telescopic
onion routing}. Circuits are built incrementally, obtaining a session key from
each successive relay in the circuit and encrypting messages so that
intermediate relays are unable to decrypt the message. Since circuits can take
some time to build, they are pre-emptively created at regular intervals
\parencite[p. 5]{Dingledine:2004p314}. Although Tor does not support many of
the traffic normalization techniques that provide strong anonymity, messages
passed through the Tor network are packaged in \emph{cells} of a fixed size of
512 bytes \parencite[p. 5]{Dingledine:2004p314}. Tor also provides application
level filters that remove identifying features from common application
protocols.

@@

Like system performance, latency is also dependent on the quality of the
network. Network switching equipment has limited resources for routing packets
and competing network traffic can introduce congestion which would radically
alter the observable communications patterns \parencite{Jacobson:1995p6768}.
Tor also supports congestion mitigation techniques which alter communication
patterns \parencite[p. 8]{Dingledine:2004p314}.

@@

Tor provides communications facilities to a number of Internet enabled
applications by providing an interface using the SOCKS protocol \parencite[p.
17]{Dingledine:2004p314}. This means that the Tor network can proxy regular web
browsing, email or any other TCP or UDP based communication protocol
\parencite{website:socks}. Each of these application protocols have their own
distinguishing communications characteristics which will influence the matching
algorithm. It is not yet clear how transparent the Tor network will be
regarding these characteristics and thus, for the purposes of classification a
single protocol should be chosen.

>>>>

The possibility of public key cryptography, or non-secret encryption was
conceived by James H. Ellis in \citeyear{Ellis:1970p3249} and later developed
into both a method for sharing secret encryption keys by Malcolm J. Williamson
in 1974 \parencite{Singh:1999:CBE} and a method for asymmetric encryption
\parencite{Cocks:1973p3265}.

@@

The first anonymous network system MixNet, was described in
\textcite{Chaum:1981p296}. This proposal makes essential usage of public key
encryption to prevent eavesdroppers from obtaining message delivery information.
Senders in the network communicate with a centrally located server known as a
mix, delivering a message with the address of the intended recipient. The mix
server discards any information about the sender and delivers it to the final
destination. Figure \ref{chaums-mix-network} depicts the process of message
delivery in Chaum's MixNet. Chaum's proposal also allowed for the chaining of
multiple mix servers together to form a cascade.

@@

\begin{itemize*}
  \item Anonymous remailers such as Babel \parencite{Gulcu:1996p1662} and
    Mixminion \parencite{Danezis:2003ys}.
  \item Networks that provide mathematically provable anonymity
    \parencite{Chaum:1988p5869,Waidner:1989p5870,Berman:2004p303}.
  \item Anonymity that degrades gracefully when subject to attack, so called
    robust anonymity \parencite{Waidner:1989p5870,Jakobsson:1998p5137}.
  \item Anonymous publishing in Freedom \parencite{Goldberg:1999p2231} and
    Freenet \parencite{Clarke:2001p2435}.
  \item Peer to Peer (P2P) anonymity such as MorphMix
    \parencite{Rennhard:2002p4559}, Tarzan \parencite{Freedman:2002kx} and P5
    \parencite{P5Sherwood:2005p5872}.
  \item Censorship resistance in aChord and gnuNet \parencite{Hazel:2002p6929},
    Infranet \parencite{Feamster:2002p307} and of course Tor.
\end{itemize*}

@@

Like MixNet, public key cryptography is combined with intermediate servers
responsible for message delivery to provide a degree of anonymity. In Tor,
these mixes are known as relays and are typically chained together to
construct a circuit. Clients connect to the Tor network by communicating
with a special relay known as a bridge, which constitutes the first
relay in a circuit. Traffic is repeatedly delivered through relays until it
reaches another special relay known as an exit node, where it is
delivered unencrypted to the final destination. Figure \ref{tor-network} shows
this typical usage of the Tor network.

@@

Messages delivered through the Tor network are encrypted multiple times using a
variation of onion routing \parencite{Michael:2001} known as telescopic onion
routing. Circuits are built incrementally, obtaining a session key from each
successive relay in the circuit and encrypting messages so that intermediate
relays are unable to decrypt the message. Since circuits can take some time to
build, they are pre-emptively created at regular intervals
\parencite[5]{Dingledine:2004p314}. Although Tor does not support many of the
traffic normalization techniques that provide strong anonymity, messages passed
through the Tor network are packaged in cells of a fixed size of 512 bytes
\parencite[5]{Dingledine:2004p314}. Tor also provides application level filters
that remove identifying features from common application protocols.

@@

Like system performance, latency is also dependent on the quality of the
network. Network switching equipment has limited resources for routing packets
and competing network traffic can introduce congestion which would radically
alter the observable communications patterns \parencite{Jacobson:1995p6768}.
Tor also supports congestion mitigation techniques which alter communication
patterns \parencite[8]{Dingledine:2004p314}.

@@

Tor provides communications facilities to a number of Internet enabled
applications by providing an interface using the SOCKS protocol
\parencite[17]{Dingledine:2004p314}. This means that the Tor network can proxy
regular web browsing, email or any other TCP or UDP based communication protocol
\parencite{website:socks}. Each of these application protocols have their own
distinguishing communications characteristics which will influence the matching
algorithm. It is not yet clear how transparent the Tor network will be regarding
these characteristics and thus, for the purposes of classification a single
protocol should be chosen.
